\hydrogen{} and \carbon{} Network Strategies for the European Energy System

### 2023-12-21 report/submissions/journal/paper/paper.tex
add pypsa and linopy refs and BE acknowledgement

The study is conducted based on the open-source, capacity expansion model PyPSA-Eur~\cite{horschPyPSAEurOpenOptimisation2018,brownSynergiesSectorCoupling2018,PyPSAEurSecSectorCoupledOpen2023}.
The model uses the open-source software tools PyPSA~\cite{brownPyPSAPythonPower2018} and Linopy~\cite{hofmannLinopyLinearOptimization2023} for modelling and cost-optimization.
The model optimizes the design and operation of the European energy system, encompassing the power, heat, industry, agriculture, and transport sectors, including international aviation and shipping.
All technology cost assumptions are taken for the year 2040 and sourced from an open-source database~\cite{lisazeyenPyPSATechnologydataTechnology2023}.
Many of the assumptions contained therein are based on the technology catalogues published by the Danish Energy Agency~\cite{danishenergyagencyTechnologyDataGeneration2019,thedanishenergyagencyTechnologyDataCarbon2023}.
Endogenous model results include the expansion of renewable energy sources, storage technologies, power-to-X conversion and transmission capacities, heating technologies, peaking power plants, and the deployment of gray, blue or green hydrogen, among others.
The model considers various energy carriers like electricity, heat, hydrogen, methane, methanol, liquid hydrocarbons and biomass, together with the corresponding conversion technologies.

@@

>>>>

The study is conducted based on the open-source, capacity expansion model PyPSA-Eur~\cite{horschPyPSAEurOpenOptimisation2018,brownSynergiesSectorCoupling2018,PyPSAEurSecSectorCoupledOpen2023}.
The model uses the open-source software tools PyPSA~\cite{brownPyPSAPythonPower2018} and Linopy~\cite{hofmannLinopyLinearOptimization2023}
for modelling and cost-optimization.
The model optimizes the design and operation of the European energy system, encompassing the power, heat, industry, agriculture, and transport sectors, including international aviation and shipping.
All technology cost assumptions are taken for the year 2040 and sourced from an open-source database~\cite{lisazeyenPyPSATechnologydataTechnology2023}.
Many of the assumptions contained therein are based on the technology catalogues published by the Danish Energy Agency~\cite{danishenergyagencyTechnologyDataGeneration2019,thedanishenergyagencyTechnologyDataCarbon2023}.
Endogenous model results include the expansion of renewable energy sources, storage technologies, Power-To-X conversion and transmission capacities, heating technologies, peaking power plants, and the deployment of gray, blue or green hydrogen, among others.
The model considers various energy carriers like electricity, heat, hydrogen, methane, methanol, liquid hydrocarbons and biomass, together with the corresponding conversion technologies.

@@

\subsection*{Acknowledgements}

Fabian Hofmann and Christoph Tries are funded by the BreakthroughEnergy Initiative~\cite{BreakthroughEnergy2023}.
